(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-09 table_fpp.tex
blah
table typo
sorting

\begin{deluxetable*}{lcccccc}

@@

\label{Tab:FPP}}

@@

@@

@@

@@

 \cellcolor{red} $201257461$  & \cellcolor{red}  $1$  & \cellcolor{red}  $0.59$  & \cellcolor{red}  $< 10^{-4}$  & \cellcolor{red}  $0.072$  & \cellcolor{red}  $0.93$  & \cellcolor{red}  $0.22$  & \cellcolor{red}  $1$\\

@@

 \cellcolor{red} $201565013$  & \cellcolor{red}  $1$  & \cellcolor{red}  $1.69$  & \cellcolor{red}  $0.0023$  & \cellcolor{red}  $0.14$  & \cellcolor{red}  $0.82$  & \cellcolor{red}  $0.07$  & \cellcolor{red}  $0.96$\\

@@

$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ \\
 \cellcolor{red} $201649426$  & \cellcolor{red}  $1$  & \cellcolor{red}  $3.10$  & \cellcolor{red}  $0.81$  & \cellcolor{red}  $0.0016$  & \cellcolor{red}  $0.13$  & \cellcolor{red}  $0.01$  & \cellcolor{red}  $0.94$\\
 \cellcolor{red} $201505350$  & \cellcolor{red}  $1$  & \cellcolor{red}  $2.69$  & \cellcolor{red}  $< 10^{-4}$  & \cellcolor{red}  $0.13$  & \cellcolor{red}  $0.86$  & \cellcolor{red}  $0.18$  & \cellcolor{red}  $0.99$\\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$

>>>>

\begin{deluxetable*}{lccccccc}

@@

\label{Tab:FPP}

@@

 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$\\

@@

 \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.13$  & \color{red}  $0.86$  & \color{red}  $0.18$  & \color{red}  $0.99$\\
 \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$\\

@@

 \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.81$  & \color{red}  $0.0016$  & \color{red}  $0.13$  & \color{red}  $0.01$  & \color{red}  $0.94$\\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\

@@

@@

@@

$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$
